---
title: "Untitled"
output: html_document
---

```{r}
library(data.table)
library(readr)
library(tidyverse)
```


# read bim file of japonica array
```{r}

bim <- fread('/mnt/share6/FOR_Takeo/Japanese_PC/tohokuonly_20160704_maf0001.bim')

```


# make columns for annovar 
```{r}

bim1 <- bim %>% 
  mutate(Start = V4, nagasa = nchar(V5)-1) %>% 
  mutate(End = Start + nagasa) %>% 
  dplyr::select(V1,Start,End,V5,V6,V2)
```

# split bim1 into each chromosome
```{r}

for (i in 1:22){
  outname = paste0('/mnt/share6/FOR_Takeo/Japanese_PC/annotation/chr',i,'bim.txt')
  tmp_bim <- bim1 %>% 
    filter(V1 == i)
  
  tmp_bim %>% 
    write_tsv(outname,col_names = FALSE)
}
```


# then run annovar 
cd /mnt/share6/Annotation\ files/ichip_v2_v1_annovar_annotation_25_jul_2018

for i in `seq 1 22`;
do
file_name="/mnt/share6/FOR_Takeo/Japanese_PC/annotation/chr"$i"bim.txt"
out_name="/mnt/share6/FOR_Takeo/Japanese_PC/annotation/annotated_file/chr"$i

annovar/table_annovar.pl ${file_name} humandb/ \
-buildver hg19 \
-out ${out_name} \
-remove \
-protocol refGene,knownGene,ensGene,dbnsfp33a,intervar_20180118,gnomad_exome,gnomad_genome,mcap,revel,avsnp150,cadd13gt20 \
-operation g,g,g,f,f,f,f,f,f,f,f \
-nastring . -polish --thread 20
done
